\cleardoublepage

\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

It has been a long and unusual journey to finally come to submitting my thesis. As with anything such as this, it would not have been possible without the help of a hoard of disparate delightful humans. The first I'd like to acknowledge of course is my supervisor, Robert Mokaya. From the beginning (prior to my master's research) you have accepted and encouraged every half-planned route of investigation I've decided to go down. I look forward to continuing to work with you. I'm also grateful to all current and former members of the Mokaya group, but in particular Alison Taylor who trained me on many synthetic and analytical techniques as well as Thria Alkhaldi with whom it is always fun to discuss ideas for experiments. I'd like to thank the technical staff in the School of Chemistry, in particular Mark Guyler and Neil Barnes for their essentially help and calm heads when things (frequently!) break, or indeed when I break them even worse than they were originally broken. Neil also provided a vital listening ear when I was extremely stressed and frustrated in my second year. On that topic, thanks to everyone who frequents the school smoking area for allowing me to vent when needed.

Outside of the University of Nottingham, I'd like to thank Jacek Jagiello for taking an avid interest in my work and the many chats we had about adsorption theory. In a similar vein, discussions with Paul Iacomi have always been so insightful. He alongside Hassan Akhtar have been a great help in improving my infantile computer code at times. More recently, abstract mathematical discussions with my dear \textgreek{Ηρώ} have been great fun and helped me look at my work in a different way. Two broad groups of friends that may not have donated technical knowledge but lent more emotional support are those at Kunsthaus and its extended universe, and the Whitchurch OGs - you know who you are. From the latter group I'd like to single out my best mate Jonnie Felton, and from the former Raffa and Mattia who have patiently listened to me babble about some incoherent abstract concept for which I have not armed them adequately with the prerequisite knowledge.

I'd further like to acknowledge Alexandra Elbakyan for her work in liberating scientific literature with sci-hub. This work, and indeed my research in general would be much more difficult if not impossible without her persistent fight against the greed of the scientific publishing industry. Similarly I thank all who have laid groundwork, and worked tirelessly with the goal of a more open scientific ecosystem including such figures as Mike Morrison and the late Aaron Swartz.

I suppose that just leaves my family. My younger sisters have all served as cheerleaders in their own right and I'm thankful for all three of you. Aunt Mimi and Grandma Joy you've always told me I can be anything I want to be and that has inspired (an at times dangerous) amount of self-confidence which has pushed me through this PhD. But the biggest thanks goes to my mother Cheryl. Apart from preventing me from dying at various points before I was five and being a great Mom in general you literally taught me how to read and write, so none of this would be possible without you. You inspired and encouraged a lifelong love of learning in me and that is truly something that money cannot buy. 